Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-12 emsoft-2019/Error_Analysis.tex
fixing section 4.3

In this section, we present our error analysis assuming that a fixed-point word lengths is given.
Then in the next section, we explain our optimization algorithm which determines suitable word
lengths fully automatically.% in~\autoref{sec:Controller_Synthesis}.
While we do not employ the error analysis independently of the controller and
precision synthesis, we note that it is an alternative way of bounding errors to
existing methods~\cite{imperialrmpc}.
\Sadegh{Alternative in what sense? What is the major difference between our analysis and \cite{imperialrmpc}?}

@@

%The incorrect region error (\autoref{eq:maximization}) is computed using Matlab's multi-parametric toolbox. 
Due to the affinity of function
$v_{i}-v_{j}$, and because we defined the tube as a convex region surrounding the corresponding hyperplane, it suffices
to evaluate the function only at the corner points of the tube, and keep the
result with the maximal magnitude. To evaluate the point location error across the corner points, we need to first locate the corner points as well as all the regions which share those corner points. We start by computing the vertices for each region $R_i$ by converting the convex set of constraint inequalities for that region into the set of vertices at the intersections of those inequalities using existing tools such as $\mathit{lcon2vert}$ written for MATLAB (\cite{????}). The computed vertex $v_i$ will be associated with a $n-D$ hypercube with the edge length of $2 \varepsilon$. Each of the $2^n$ vertices of this hypercube is counted as a corner point. In order to find out which regions have the same vertex $v_i$, one approach is to compute and save the set of vertices for all the regions and then to find out the neighboring regions via exhaustive search with the saved set of vertices. Alternatively, for the vertex $v_i$, all the regions $R_j$s having $v_i$ as their vertex can be identified if at least $n$ of their hyperplanes cross $v_i$. We used both approaches; however, the later scales up better when we have millions of vertices. In brief, we go through these steps: (i) for each region, the set of vertices are computed; (ii) for the vertex $v_i$, the set of all regions $\mathcal R_{ij}$ having $v_i$ as their own vertex are found; (iii) for the vertex $v_i$, the set of corner points $v_{ik}$ are computed which form a hypercube centering at $v_i$; (iv) for every corner point $c_k=v_{ik}$ and for every pair $(\mathcal R_{ij1},\mathcal R_{ij_2})$, the corresponding corner error $|v_{j1}-v_{j2}|$ is computed; (v) finally, we pick the greatest corner error.

\eva{This needs more details. Which function(s) and algorithm from Matlab are used?}
\eva{How do you determine which regions are neighbors? resp. which borders are matching?}

$\varepsilon_Q$ and $err(v_{i})_{p}$ are computed by Daisy. For this we encode
the expressions in~\autoref{eq:quantizationlines} and \autoref{eq:fperror}
respectively as straight-line arithmetic expressions and specify the constraints
on the domain of $\statevar$ in the precondition.
Daisy performs a dataflow analysis to determine the finite-precision roundoff
errors. This error computation differs from the one employed by
\citet{imperialrmpc} which phrases the roundoff error computation as a (relaxed)
mixed integer programming problem.

>>>>

In this section, we present our error analysis assuming that a fixed-point word lengths is given.
Then in the next section, we explain our optimization algorithm which determines suitable word
lengths fully automatically.% in~\autoref{sec:Controller_Synthesis}.
While we do not employ the error analysis independently of the controller and
precision synthesis, we note that it is an alternative way of bounding errors to
existing methods~\cite{imperialrmpc}, which phrase the roundoff error computation as a (relaxed)
mixed integer programming problem.
%\Sadegh{Alternative in what sense? What is the major difference between our analysis and \cite{imperialrmpc}?}

@@

The incorrect region error (\autoref{eq:maximization}) is computed with Matlab.

Due to the affinity of function
$v_{i}-v_{j}$, and because we defined the tube as a convex region surrounding the corresponding hyperplane, it suffices
to evaluate the function only at the corner points of the tube, and keep the
result with the maximal magnitude. 
To evaluate the incorrect region selection error across
the corner points, we need to first locate the corner points as well as all the
regions which share those corner points. 
Each region $R_i$ is represented by a set of contraints. We first extract the
set of vertices of $R_i$ using the open source Matlab library
$\mathit{lcon2vert}$~\cite{??}.
For each computed vertex $v_i$, we compute a $n-D$
hypercube with the edge length of $2 \varepsilon$. 
Each of the $2^n$ vertices of this hypercube is counted as a corner point, on which
we evaluate $\|u_i - u_j\|$.

In order to find out which regions share a vertex $v_i$, we implemented two approaches.
The first approach determines the set of neighboring regions via an exhaustive
search over the set of vertices. However, we observed that this algorithm only
scales to small numbers of regions.
Our second approach works on the observation that all the regions $R_j$s 
having $v_i$ as their vertex can be identified if at least $n$ of their hyperplanes cross $v_i$.

% In brief, we go
% through these steps: (i) for each region, the set of vertices are computed; (ii)
% for the vertex $v_i$, the set of all regions $\mathcal R_{ij}$ having $v_i$ as
% their own vertex are found; (iii) for the vertex $v_i$, the set of corner points
% $v_{ik}$ are computed which form a hypercube centering at $v_i$; (iv) for every
% corner point $c_k=v_{ik}$ and for every pair $(\mathcal R_{ij1},\mathcal
% R_{ij_2})$, the corresponding corner error $|v_{j1}-v_{j2}|$ is computed; (v)
% finally, we pick the greatest corner error.

% \eva{This needs more details. Which function(s) and algorithm from Matlab are used?}
% \eva{How do you determine which regions are neighbors? resp. which borders are matching?}

$\varepsilon_Q$ and $err(v_{i})_{p}$ are computed by Daisy. For this we encode
the expressions in~\autoref{eq:quantizationlines} and \autoref{eq:fperror}
respectively as straight-line arithmetic expressions and specify the constraints
on the domain of $\statevar$ in the precondition.
Daisy performs a dataflow analysis to determine the finite-precision roundoff
errors. 
% This error computation differs from the one employed by
% \citet{imperialrmpc} which phrases the roundoff error computation as a (relaxed)
% mixed integer programming problem.
